---
title: "HW 8"
author: "Alexa Monachino"
date: "`r Sys.Date()`"
format: pdf
---

```{r, echo=F}
#| message: false
#| echo: false
#| output: false
library(cmdstanr)  # use two cores
library(bayesplot)

# Determine list of packages:
list.of.packages <- c("psych", "reshape2", "car", "ggplot2", "tidyr", "dplyr", "foreach", "doParallel", "R.matlab", "brms", "modelsummary", "posterior", "readxl", "here")

# Install any packages that are not installed already:
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Load packages
lapply(list.of.packages, require, character.only = TRUE)
```

# Research Question

> Is there difference in infant attention, as measured by signal-to-noise ratio, to different affective expressions?

# Variables

- `id`/`record_id`: Participant ID number
- `variable`: affect condition with the following options: Neutral, Happy, Angry, Fear
- `value`: SNR, measure of attention

## Data Import

```{r}
snr <- read_excel(here("data_files", "ssVEP_Bayes.xlsx"))
snr$variable <- relevel(as.factor(snr$variable), ref="Neutral")
```

## Variable Summary

Table @tbl-summ-var shows the summary statistics of evaluation ratings by groups.

```{r}
#| message: false
#| echo: false
#| label: tbl-summ-var
#| tbl-cap: Descriptive statistics by groups
datasummary(value  * 
                (N + Mean + SD + Min + Max + Histogram) ~ 
                factor(variable, labels = c("Neutral", "Happy", "Angry", "Fear")),
            data = snr)
```

# Model

Model:
$$
  \begin{aligned}
    Value_{variable, id} & \sim N(\mu_{variable, id}, \sigma) \\ 
    \mu_{variable, id} & \sim N(\gamma_{variable},\tau)
  \end{aligned}
$$

Prior:
$$
  \begin{aligned}
  
    \gamma & \sim N(0, 2.5) for all categories \\
    \sigma & \sim t^+(3, 0, 2.5) \\
    \tau & \sim t^+(3, 0, 2.5)
  \end{aligned}
$$

## Analysis

We used 4 chains, each with 4,000 iterations (first 2,000 as warm-ups). 

```{r}
#| message: false
#| echo: false
#| output: false
mod <- brm(value ~ variable + (1 | record_id),
           data = snr,
           iter = 4000,
           prior = prior(normal(0, 2.5), class = "b"),
           save_pars = save_pars(all = TRUE),
           seed = 1234)
```

# Results

As shown in the trace plots in @fig-trace-fit below, the chains mixed well.

```{r}
#| message: false
#| echo: false
#| label: fig-trace-fit
#| fig-cap: Trace plot of the posterior distributions of model parameters.
mcmc_plot(mod, type = "trace")
```

@tbl-summ-fit shows the posterior distributions.

```{r}
#| message: false
#| echo: false
#| label: tbl-summ-fit
#| tbl-cap: Posterior summary of the model parameters.
mod_draws <- summarize_draws(mod)[1:6,]
mod_draws
```

The analysis showed that on average, infants paid the most attention to fearful faces compared to all other faces with a posterior mean of `r round(mod_draws$mean[2], 2)` and a 90% CI of [`r round(mod_draws$q5[2], 2)`, `r round(mod_draws$q95[2], 2)`]. Infants also paid more attention to happy faces than to neutral faces with a posterior mean of `r round(mod_draws$mean[3], 2)` and a 90% CI of [`r round(mod_draws$q5[3], 2)`, `r round(mod_draws$q95[3], 2).

